Cover Letter: Cudele (Paper 306)

### 2018-01-09 paper/cover_letter.tex
paper: typos and revision 2
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We thank the reviewers for their hard work and genuinely helpful suggestions.
In addition to this cover letter, we have posted a
\href{https://github.com/michaelsevilla/cudele-popper/blob/master/paper/diff.pdf}{PDF
online} explicitly showing additions in \textcolor{blue}{\textbf{blue}} and
deletions in \textcolor{red}{\textbf{red}}. Three issues were common across
reviewer feedback; Reviewer 1 and 3's comments are addressed in issues II and
III, Reviewer 2's comments are addressed in issues I and III, and Reviewer 4's
comments are addressed in issues I and II.

@@

To align the paper to the themes of the conference, we changed Section~{\S}V-A
and Figures 6a, 6b, and 6c to emphasize that decoupled namespaces facilitate
client-driven parallelism, where clients detach subtrees form the global namespaces
and do operations in-parallel to their local disk. We also hope that changes to
the use cases above motivate the need for robust distributed storage systems
that can handle today's applications.  So while the paper is storage-centric,
we try to show that the workloads it supports are highly distributed and need a
flexible solution like Cudele.

@@

  \item explicitly state Cudele setups and subtree configurations in bold in
Section~{\S}V-B to guide the reader through use cases and the effects of
different Cudele API configurations.

@@

  \item clarified confusing terminology in Section~{\S}II: administrator refers
to a person that configures subtrees and client refers to a storage client or
application that interacts with the metadata server. We avoid using the term
``user" except when referring to end-users that interact with home directories
in a file system or the Hadoop/Spark runtime itself.

@@

We apologize for the omission of experimental setup and source code details.
We made artifacts available online for all experiments in the paper. For the
experimental setup, we describe the cluster setup (hardware, software, etc.) in
Section~{\S}V.  We have also made the infrastructure code available and added
links after each figure to show exactly how experiments are run.  This
infrastructure code contains scripts to deploy the system, run experiments, and
gather results.  This process follows the \href{http://falsifiable.us/}{Popper
Convention}, which aims to make research reproducible.  We also made the source
code available online and a link is provided in Section~{\S}V. Finally, we add
details about which tools and classes we modified in Section~{\S}IV to address
Reviewer 1's questions about the framework implementation.

@@

For Reviewer 1, we fixed user/client terminology in Section~{\S}III,
clarified that the cost of dynamically changing semantics is future work in
Sections~{\S}I and~{\S}III, and added source code pointers in Section~{\S}V.
For Reviewer 2, we removed the major takeaways headings and cross-references in
Section~{\S}V. For Reviewer 3, we quantified speedups with figure annotations
in Section~{\S}V. For Reviewers 1 and 3, we added servers, network, and storage
setups in Section~{\S}V. For Reviewer 4 we added descriptions to each use case
in Section~{\S}V describing how Cudele would work with Spark.

>>>>

We thank the reviewers for their hard work and genuinely helpful suggestions.
In addition to this cover letter, we have posted a
\href{https://github.com/michaelsevilla/cudele-popper/blob/master/paper/diff.pdf}{PDF
online} explicitly showing additions in \textcolor{blue}{\textbf{blue}} and
deletions in \textcolor{red}{\textbf{red}}. Three issues were common across
reviewer feedback; Reviewer 1 and 3's comments are addressed in issues II and
III, Reviewer 2's comments are addressed in all issues, and Reviewer 4's
comments are addressed in issues I and II.

@@

To align the paper to the themes of the conference, we changed Section~{\S}V-A
and Figures 6a, 6b, and 6c to emphasize that decoupled namespaces facilitate
client-driven parallelism, where clients detach subtrees form the global namespace
and do operations in-parallel to their local disk. We also hope that changes to
the use cases above motivate the need for robust distributed storage systems
that can handle today's applications.  So while the paper is storage-centric,
we try to show that the workloads it supports are highly distributed and need a
flexible solution like Cudele.

@@

%  \item explicitly state Cudele setups and subtree configurations in bold in
%Section~{\S}V-B to guide the reader through use cases and the effects of
%different Cudele API configurations.

@@

  \item clarified confusing terminology in Section~{\S}I: administrator refers
to a person that configures subtrees and client refers to a storage client or
application that interacts with the metadata server. We avoid using the term
``user" except when referring to end-users that interact with home directories
in a file system or the Hadoop/Spark runtime itself.

@@

We apologize for the omission of experimental setup and source code details.
For the experimental setup, we describe the cluster setup (hardware, software,
etc.) in Section~{\S}V.  We have also made the infrastructure code available
and added links after each figure to show exactly how experiments are run.
This infrastructure code contains scripts to deploy the system, run
experiments, and gather results.  This process follows the
\href{http://falsifiable.us/}{Popper Convention}, which aims to make research
reproducible.  We also made the source code available online and a link is
provided in Section~{\S}V. Finally, we add details about which tools and
code bases we modified in Section~{\S}IV to address Reviewer 1's questions about
the framework implementation.

@@

For Reviewer 1, we fixed user/client terminology in Section~{\S}III,
clarified that the cost of dynamically changing semantics is future work in
Sections~{\S}I and~{\S}III, and added source code pointers in Section~{\S}V.
For Reviewer 2, we removed the major takeaway headings and cross-references in
Section~{\S}V. For Reviewer 3, we quantified speedups with figure annotations
in Section~{\S}V. For Reviewers 1 and 3, we added servers, network, and storage
setups in Section~{\S}V. For Reviewer 4, we added descriptions to each use case
in Section~{\S}V describing how Cudele would work with Spark.

### 2018-01-09 paper/sections/0_abstract.tex
paper: typos and revision 2
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

HPC and data center scale application developers are abandoning POSIX IO
because file system metadata synchronization and serialization overheads of
providing strong consistency and durability are too costly -- and often
unnecessary -- for their applications.  Unfortunately, designing file systems
with weaker consistency or durability semantics excludes applications that rely on
stronger guarantees, forcing developers to re-write their applications or
deploy them on a different system.  We present a framework and API that lets
\oldcomment{clients}\newcomment{administrators} specify their
consistency/durability requirements and dynamically assign them to subtrees in
the same namespace, allowing administrators to optimize subtrees over time and
space for different workloads. \oldcomment{By custom fitting a subtree to a
create-heavy application,} We show similar speedups to related work but more
importantly, \oldcomment{our prototype can custom fit subtrees in the same
namespace to applications common in large data centers, }\newcomment{ we show
performance improvements when we custom fit subtree semantics to applications
such as checkpoint-restart (91.7\(\times\) speedup), user home directories
(0.03 standard deviation from optimal), and users checking for partial results
(2\% \oldcomment{clients}\newcomment{users} overhead).} \oldcomment{ and can
scale to 2\(\times\) as many clients when compared to our baseline system.}

>>>>

HPC and data center scale application developers are abandoning POSIX IO
because file system metadata synchronization and serialization overheads of
providing strong consistency and durability are too costly -- and often
unnecessary -- for their applications.  Unfortunately, designing file systems
with weaker consistency or durability semantics excludes applications that rely
on stronger guarantees, forcing developers to re-write their applications or
deploy them on a different system.  We present a framework and API that lets
\oldcomment{clients}\newcomment{administrators} specify their
consistency/durability requirements and dynamically assign them to subtrees in
the same namespace, allowing administrators to optimize subtrees over time and
space for different workloads. \oldcomment{By custom fitting a subtree to a
create-heavy application,} We show similar speedups to related work but more
importantly, \oldcomment{our prototype can custom fit subtrees in the same
namespace to applications common in large data centers, }\newcomment{ we show
performance improvements when we custom fit subtree semantics to applications
such as checkpoint-restart (91.7\(\times\) speedup), user home directories
(0.03 standard deviation from optimal), and users checking for partial results
(2\% overhead).} \oldcomment{ and can scale to 2\(\times\) as many clients when
compared to our baseline system.}

### 2018-01-09 paper/sections/1_introduction.tex
paper: typos and revision 2
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What is the problem?
File system metadata services in HPC and large-scale data centers have
scalability problems because common tasks, like
checkpointing~\cite{bent_plfs_2009} or scanning the file
system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every \newcomment{client} is unreasonable. This problem is
exacerbated by current hardware and software trends: parallel runtimes like
Hadoop and Spark use storage systems to implement important scheduling and
timing semantics, and  \oldcomment{; for example, } HPC architectures are
transitioning from complex storage stacks with burst buffer, file system,
object store, and tape tiers to more simplified stacks with just a burst buffer
and object store~\cite{bent:login16-hpc-trends}. These types of trends put
pressure on data access because more requests from different nodes end up
hitting the same layer in parallel and latencies cannot be hidden while data
migrates across tiers.

@@

% One example
One popular approach for relaxing consistency and durability is to ``decouple
the namespace", where clients lock the subtree they want exclusive access to as
a way to tell the file system that the subtree is important or may cause
resource contention in the near-future~\cite{grider:pdsw2015-marfs,
zheng:pdsw2015-deltafs, zheng:pdsw2014-batchfs, ren:sc2014-indexfs,
bent:slides-twotiers}. Then the file system can change its internal structure
to optimize performance. For example, the file system could enter a mode that
prevents other clients from interfering with the decoupled directory.  This
delayed merge ({\it i.e.} a form of eventual consistency) and relaxed
durability improves performance and scalability by avoiding the costs of remote
procedure calls (RPCs), synchronization, false sharing, and serialization.
While the performance benefits of decoupling the namespace are obvious,
applications that rely on the file system's guarantees must be deployed on an
entirely different system or re-written to coordinate strong
consistency/durability themselves.

@@

  \oldcomment{This framework lets subtrees with different semantics co-exist in
a global namespace. We show how this} \newcomment{We show how that letting
different semantics co-exist in a global namespace scales further and performs
better than systems that use one strategy.}

@@

% Results
The results in this paper confirm the assertions of ``clean-state" research of
decoupled namespaces; specifically that these techniques drastically improve
performance.  We go a step further by quantifying the costs of merging updates
(3.37\(\times\) slowdown) and maintaining durability (\(2.4\times\) slowdown).
In our prototype, \newcomment{we also show how to assign subtree semantics for
certain applications such as checkpoint-restart (\(91.7\times\) speedup if
consistency is fully relaxed), user home directories (within a 0.03 standard
deviation from optimal), and end-users checking for partial results (only a 2\%
overhead).} \oldcomment{we get an 8\(\times\) speedup and can scale to twice as
many clients when we assign a more relaxed form of consistency and durability
to a subtree with a create-heavy workload.}  We use Ceph as a prototyping
platform because it is used in cloud-based and data center systems and has a
presence in HPC~\cite{wang:pdsw13-ceph-hpc}.

>>>>

% What is the problem?
File system metadata services in HPC and large-scale data centers have
scalability problems because common tasks, like
checkpointing~\cite{bent_plfs_2009} or scanning the file
system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every \newcomment{client}\footnote{In this paper, ``client"
is a storage client or application that interacts with the metadata server,
``administrator" is a system administrator that configures the storage, and
``end-users" interact with the file system via home directories or runtimes.  }
is unreasonable. This problem is exacerbated by current hardware and software
trends: parallel runtimes like Hadoop and Spark use storage systems to
implement important scheduling and timing semantics and  \oldcomment{; for
example, } HPC architectures are transitioning from complex storage stacks with
burst buffer, file system, object store, and tape tiers to more simplified
stacks with just a burst buffer and object
store~\cite{bent:login16-hpc-trends}. These types of trends put pressure on
data access because more requests from different nodes end up hitting the same
layers in parallel\oldcomment{and latencies cannot be hidden while data
migrates across tiers}.

@@

% One example
One popular approach for relaxing consistency and durability is to ``decouple
the namespace", where clients lock the subtree they want exclusive access to as
a way to tell the file system that the subtree is important or may cause
resource contention in the near-future~\cite{grider:pdsw2015-marfs,
zheng:pdsw2015-deltafs, zheng:pdsw2014-batchfs, ren:sc2014-indexfs,
bent:slides-twotiers}. Then the file system can change its internal structure
to optimize performance. For example, the file system could enter a mode where
clients with decoupled directories perform operations locally and bulk merge their
updates at completion. This delayed merge ({\it i.e.} a form of eventual
consistency) and relaxed durability improves performance and scalability by
avoiding the costs of remote procedure calls (RPCs), synchronization, false
sharing, and serialization.  While the performance benefits of decoupling the
namespace are obvious, applications that rely on the file system's guarantees
must be deployed on an entirely different system or re-written to coordinate
strong consistency/durability themselves.

@@

  \oldcomment{This framework lets subtrees with different semantics co-exist in
a global namespace. We show how this} \newcomment{We show that letting
different semantics co-exist in a global namespace scales further and performs
better than systems that use one strategy.}

@@

% Results
The results in this paper confirm the assertions of ``clean-slate" research of
decoupled namespaces; specifically that these techniques drastically improve
performance.  We go a step further by quantifying the costs of traditional file
system approaches to maintaining consistency (3.37\(\times\) slowdown) and
durability (\(2.4\times\) slowdown).  In our prototype, \newcomment{we also
show the benefits of assigning subtree semantics to certain applications such
as checkpoint-restart (\(91.7\times\) speedup if consistency is fully relaxed),
user home directories (within a 0.03 standard deviation from optimal), and
end-users checking for partial results (only a 2\% overhead).} \oldcomment{we
get an 8\(\times\) speedup and can scale to twice as many clients when we
assign a more relaxed form of consistency and durability to a subtree with a
create-heavy workload.}  We use Ceph as a prototyping platform because it is
used in cloud-based and data center systems and has a presence in
HPC~\cite{wang:pdsw13-ceph-hpc}.

### 2018-01-09 paper/sections/3_posix_overheads.tex
paper: typos and revision 2
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb] \centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-compile/visualize/viz.ipynb}{source}]
For the CephFS metadata server, create-heavy workloads ({\it e.g.},
\texttt{untar}) incur the highest disk, network, and CPU utilization because of
consistency/durabiliy demands.}\label{fig:overhead-creates}
\end{figure}

In our examination of the overheads of POSIX IO we benchmark and analyze
CephFS, the file system that uses Ceph's object store ({\it i.e.} RADOS) to
store its data and metadata. \newcomment{In this paper, ``client" is a storage
client or application that interacts with the metadata server, ``administrator"
is a system administrator that configures the storage, and ``end-users"
interact with the file system via home directories or runtimes.} To show how
the file system behaves under high metadata load we use a create-heavy
workload.  During this process we discovered, based on the analysis and
breakdown of costs, that durability and consistency have high overhead but we
urge the reader to keep in mind that this file system is an implementation of
one set of design decisions and our goal here is to highlight the effect that
those decisions have on performance.

%The RPCs are also serialized because the
%metadata server is single threaded; although na\"{\i}ve, this design is common
%because of the complexity of multi-threaded metadata
%servers~\cite{konstantinos:pdsw2014-lustre-metadata}.  
In this section we quantify the costs of consistency and durability in CephFS.
At the end of each subsection we compare the approach to ``decoupled
namespaces", the technique in related work that detaches subtrees from the
global namespace to relax consistency/durability guarantees. We use a
create-heavy workload for this study because it has high resource utilization,
as shown by the trace of compiling the Linux kernel in a CephFS mount in
Figure~\ref{fig:overhead-creates}.  The \texttt{untar} phase, which is
characterized by many creates, has the highest resource usage (combined CPU,
network, and disk) on the metadata server because of the number of RPCs needed
for consistency and durability.

@@

% Effects on performance
Figure~\ref{fig:overhead-a} shows the effect of journaling with different
\oldcomment{segment sizes; the larger the segment size the bigger that the
writes into the object store are}\newcomment{dispatch sizes, normalized to 1
client that creates 100K files with journaling off (about 654 creates/sec). In
this case a dispatch size of 10 degrades performance the most because the
metadata server is overloaded with requests and cannot spare cycles to manage
concurrent segments.  Tuning and parameter sweeps show that a dispatch size of
10 is the worst and that larger sizes approach a dispatch size of 1; for all
future journal experiments we use a dispatch size of 40 which is a more
realistic configuration.  Although the ``no journal" curve appears flat, it is
actually a slowdown of about \(0.3\times\) per concurrent client; this slowdown
is a result of the peak throughput of a single metadata server, which we found
to be about 3000 operations per second}.  The trade-off for better performance
is memory consumption because a larger
\oldcomment{segment}\newcomment{dispatch} size uses more space for buffering.
\oldcomment{When journaling is on, the metadata server periodically stops serving requests
to flush ({\it i.e.} apply journal updates) to the metadata store.  The journal
overhead is sufficient enough to slow down metadata throughput but not so much
as to overwhelm the bandwidth of the object store.}

@@

\textbf{Comparison to decoupled namespaces}: Decoupled namespaces
merge batches of metadata operations into the global namespaces when the job
completes.  In BatchFS the merge is delayed by the application using an API to
switch between asynchronous and synchronous mode. The merge itself is explicitly
managed by the application but future work looks at more automated
methodologies. In DeltaFS snapshots of the metadata subtrees stays on the client
machines; there is no ground truth and consistent namespaces are constructed
and resolved at application read time or when a 3rd party system ({\it e.g.},
middleware, scheduler, etc.) needs a view of the metadata. As a result, all the
overheads of maintaining consistency that we showed above are delayed until the
merge phase.

>>>>

\begin{figure}[tb] \centering
\includegraphics[width=1\linewidth]{./graphs/overhead-creates.png}
\caption{[\href{https://github.com/michaelsevilla/cudele-popper/blob/master/experiments/baseline-compile/visualize/viz.ipynb}{source}]
For the CephFS metadata server, create-heavy workloads ({\it e.g.},
\texttt{untar}) incur the highest disk, network, and CPU utilization because of
consistency/durability demands.}\label{fig:overhead-creates}
\end{figure}

In our examination of the overheads of POSIX IO we benchmark and analyze
CephFS, the file system that uses Ceph's object store (RADOS) to
store its data/metadata and a metadata server cluster to service client requests
more quickly.  During this process we discovered, based on the analysis and
breakdown of costs, that durability and consistency have high overhead but we
urge the reader to keep in mind that this file system is an implementation of
one set of design decisions and our goal here is to highlight the effect that
those decisions have on performance.  At the end of each subsection we compare
the approach to ``decoupled namespaces", the technique in related work that
detaches subtrees from the global namespace to relax consistency/durability
guarantees.

%The RPCs are also serialized because the
%metadata server is single threaded; although na\"{\i}ve, this design is common
%because of the complexity of multi-threaded metadata
%servers~\cite{konstantinos:pdsw2014-lustre-metadata}.

We use a create-heavy workload for this study because it has high resource
utilization, as shown by the trace of compiling the Linux kernel in a CephFS
mount in Figure~\ref{fig:overhead-creates}.  The \texttt{untar} phase, which is
characterized by many creates, has the highest resource usage (combined CPU,
network, and disk) on the metadata server because of the number of RPCs needed
for consistency and durability.

@@

% Effects on performance
Figure~\ref{fig:overhead-a} shows the effect of journaling with different
\oldcomment{segment sizes; the larger the segment size the bigger that the
writes into the object store are}\newcomment{dispatch sizes, normalized to 1
client that creates 100K files with journaling off (about 654 creates/sec). In
this case a dispatch size of 30 degrades performance the most because the
metadata server is overloaded with requests and cannot spare cycles to manage
concurrent segments.  Tuning and parameter sweeps show that a dispatch size of
10 is the worst and that larger sizes approach a dispatch size of 1; for all
future journal experiments we use a dispatch size of 40 which is a more
realistic configuration.  Although the ``no journal" curve appears flat, it is
actually a slowdown of about \(0.3\times\) per concurrent client; this slowdown
is a result of the peak throughput of a single metadata server, which we found
to be about 3000 operations per second}.  The trade-off for better performance
is memory consumption because a larger
\oldcomment{segment}\newcomment{dispatch} size uses more space for buffering.
\oldcomment{When journaling is on, the metadata server periodically stops serving requests
to flush ({\it i.e.} apply journal updates) to the metadata store.  The journal
overhead is sufficient enough to slow down metadata throughput but not so much
as to overwhelm the bandwidth of the object store.}

@@

\textbf{Comparison to decoupled namespaces}: Decoupled namespaces
merge batches of metadata operations into the global namespaces when the job
completes.  In BatchFS, the merge is delayed by the application using an API to
switch between asynchronous and synchronous mode. The merge itself is explicitly
managed by the application but future work looks at more automated
methodologies. In DeltaFS, snapshots of the metadata subtrees stays on the client
machines; there is no ground truth and consistent namespaces are constructed
and resolved at application read time or when a 3rd party system ({\it e.g.},
middleware, scheduler, etc.) needs a view of the metadata. As a result, all the
overheads of maintaining consistency that we showed above are delayed until the
merge phase.

### 2018-01-09 paper/sections/4_methodology.tex
paper: typos and revision 2
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

In this section we describe our API and framework that lets
\oldcomment{users}\newcomment{administrators} assign consistency and durability
semantics to subtrees in the global namespace. A \textbf{mechanism} is an
abstraction and basic building block for constructing consistency and
durability guarantees.\oldcomment{Cudele exposes these mechanisms and the
users}\newcomment{ The administrator} composes these mechanisms together to
construct \textbf{policies}.  These policies are assigned to subtrees and they
dictate how the file system should handle operations within that subtree.
Below, we describe the mechanisms (which are \underline{underlined}), the
policies, and the API for assigning policies to subtrees.

@@

\subsubsection{Mechanisms Used for Durability} \underline{Stream} is one of the
mechanisms used by default in CephFS.  Using existing configuration settings we
can turn Stream on and off.  If it is off, then the metadata servers will not
save journals in the object store. For \underline{Local Persist}, clients write
serialized log events to a file on local disk and for \underline{Global
Persist}, clients push the journal into the object store. The overheads for
both Local Persist and Global Persist is the write bandwidth of the local disk
and object store, respectively.  These persist mechanisms are part of the
library that links into the client.

@@

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum} POSIX IO-compliant systems like CephFS and IndexFS
have global consistency and durability\footnote{ IndexFS also has bulk merge
which is a form of ``weak consistency"}; DeltaFS uses ``invisible" consistency
and ``local" durability and BatchFS uses ``weak" consistency and ``local"
durability. These systems have other features that could push them into
different semantics but we assign labels here based on the points emphasized in
the papers.  To compose the mechanisms
\oldcomment{users}\newcomment{administrators} inject which mechanisms to run
and which to use in parallel using a domain specific language.  Although we can
achieve all permutations of the different guarantees in
Table~\ref{table:spectrum}, not all of them make sense. For example, it makes
little sense to do \texttt{append client journal+RPCs} since both mechanisms do
the same thing or \texttt{stream+local persist} since ``global" durability is
stronger and has more overhead than ``local" durability. The cost of each
mechanism and the semantics described above are quantified in
Sections~\S\ref{sec:microbenchmarks}.

@@

% the interface
Users control consistency and durability for subtrees by contacting a daemon in
the system called a monitor, which manages cluster state changes.  Users
present a directory path and a policies configuration that gets distributed and
versioned by the monitor to all daemons in the system. For example,
(msevilla/mydir, policies.yml) would decouple the path ``msevilla/mydir" and
would apply the policies in ``policies.yml".  The policies file supports the
following parameters (default values are in parenthesis): which consistency
model to use (\texttt{RPCs}), which durability model to use (\texttt{stream}), 
number of inodes to provision to the decoupled namespace (100), and which interfere
policy to use, {\it i.e.} how to handle a request from another client
targeted at this subtree (\texttt{allow}). The ``Consistency" and ``Durability"
parameters are compositions of mechanisms; they can be serialized (\(+\)) or
run in parallel (\(|\|\)).  ``Allocated Inodes" is a way for the application to
specify how many files it intends to create. It is a contract so that the file
system can provision enough resources for the incumbent merge and so it can
give valid inodes to other clients. The inodes can be used anywhere within the
decoupled namespace ({\it i.e.} at any depth in the subtree).  ``Interfere Policy"
has two settings: \texttt{block} and \texttt{allow}.  For \texttt{block}, any
requests to this part of the namespace returns with ``Device is busy", which
will spare the metadata server from wasting resources for updates that may get
overwritten. If the application does not mind losing updates, for example it
wants approximations for results that take too long to compute, it can select
\texttt{allow}. In this case, metadata from the interfering client will be
written and the computation from the decoupled namespace will take priority at
merge time because the results are more accurate.  Given these default values
decoupling the namespace with an empty policies file would give the application
100 inodes but the subtree would behave like the existing CephFS
implementation.

>>>>

In this section we describe our API and framework that lets
\oldcomment{users}\newcomment{administrators} assign consistency and durability
semantics to subtrees in the global namespace. A \textbf{mechanism} is an
abstraction and basic building block for constructing consistency and
durability guarantees. \oldcomment{Cudele exposes these mechanisms and the
users}\newcomment{The administrator} composes these mechanisms together to
construct \textbf{policies}.  These policies are assigned to subtrees and they
dictate how the file system should handle operations within that subtree.
Below, we describe the mechanisms (which are \underline{underlined}), the
policies, and the API for assigning policies to subtrees.

@@

\subsubsection{Mechanisms Used for Durability} \underline{Stream}, the default
setting in CephFS, saves a journal of metadata updates in the object store.
Using existing configuration settings we can turn Stream on and off.  For
\underline{Local Persist}, clients write serialized log events to a file on
local disk and for \underline{Global Persist}, clients push the journal into
the object store. The overheads for both Local Persist and Global Persist is
the write bandwidth of the local disk and object store, respectively.  These
persist mechanisms are part of the library that links into the client.

@@

% which system they represent and which are impossible
Existing, state-of-the-art systems in HPC can be represented by the cells in
Table~\ref{table:spectrum}. POSIX IO-compliant systems like CephFS and IndexFS
have global consistency and durability\footnote{ IndexFS also has bulk merge
which is a form of ``weak consistency"}; DeltaFS uses ``invisible" consistency
and ``local" durability and BatchFS uses ``weak" consistency and ``local"
durability. These systems have other features that could push them into
different semantics but we assign labels here based on the points emphasized in
the papers.  To compose the mechanisms
\oldcomment{users}\newcomment{administrators} inject which mechanisms to run
and which to use in parallel using a domain specific language.  Although we can
achieve all permutations of the different guarantees in
Table~\ref{table:spectrum}, not all of them make sense. For example, it makes
little sense to do \texttt{append client journal+RPCs} since both mechanisms do
the same thing or \texttt{stream+local persist} since ``global" durability is
stronger and has more overhead than ``local" durability. The cost of each
mechanism and the semantics described above are quantified in
Sections~\S\ref{sec:microbenchmarks}.

@@

% the interface
Users control consistency and durability for subtrees by contacting a daemon in
the system called a monitor, which manages cluster state changes.  Users
present a directory path and a policies configuration that gets distributed and
versioned by the monitor to all daemons in the system. For example,
(msevilla/mydir, policies.yml) would decouple the path ``msevilla/mydir" and
would apply the policies in ``policies.yml".

The policies file supports the following parameters (default values are in
parenthesis): which consistency model to use (\texttt{RPCs}), which durability
model to use (\texttt{stream}), number of inodes to provision to the decoupled
namespace (100), and which interfere policy to use, {\it i.e.} how to handle a
request from another client targeted at this subtree (\texttt{allow}). The
``Consistency" and ``Durability" parameters are compositions of mechanisms;
they can be serialized (\(+\)) or run in parallel (\(||\)).  ``Allocated
Inodes" is a way for the application to specify how many files it intends to
create. It is a contract so that the file system can provision enough resources
for the incumbent merge and so it can give valid inodes to other clients. The
inodes can be used anywhere within the decoupled namespace ({\it i.e.} at any
depth in the subtree).  ``Interfere Policy" has two settings: \texttt{block}
and \texttt{allow}.  For \texttt{block}, any requests to this part of the
namespace returns with ``Device is busy", which will spare the metadata server
from wasting resources for updates that may get overwritten. If the application
does not mind losing updates, for example it wants approximations for results
that take too long to compute, it can select \texttt{allow}. In this case,
metadata from the interfering client will be written and the computation from
the decoupled namespace will take priority at merge time because the results
are more accurate.  Given these default values decoupling the namespace with an
empty policies file would give the application 100 inodes but the subtree would
behave like the existing CephFS implementation.
